Loss recovery and tail loss performance in Multipath TCP

### 2016-11-21 main.tex
Update
update

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage[dvips]{graphicx}
% Title Page
\title{Loss recovery and tail loss performance in Multipath TCP}
\author{KAU}

@@

We try to understand the loss recovery and retransmission policies in state of the art MPTCP linux implementation.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth]{images/fortest.ps}
\caption{Topology used for Emulation}\label{fig1}
\end{center}
\label{prl}
\end{figure}
\begin{center}
\begin{table}
\begin{center}
\begin{tabular}{|c|cccccccccc|}
      \hline
      \multicolumn{1}{c}{} & & \\[\dimexpr-\normalbaselineskip-\arrayrulewidth]
      \textbf{Burst Size} & \multicolumn{10}{c|}{160 Packets} \\
      \hline
      \textbf{Separation Time} & \multicolumn{10}{c|}{2s} \\
      \hline

@@

\subsection{Testing with Deterministic loss patterns}
In order to understand the retransmission behavior of the Linux MPTCP implementation and to reproduce the observed retransmissions, we use a deterministic drop pattern.

@@

@@

\begin{table}[]
\centering
\caption{Tail loss scenarios with tcp.early.retrans = 3 default}
\label{ret3}
\begin{tabular}{|l|l|l|l|l|}
\hline
 testcase   & Asymmetry   & Metalevel          & Subflowlevel       &  \\\hline
Tail drop 1 & 20ms - 30ms & rexmt in same path & rexmt in same path &  \\\hline
Tail drop 2 & 30ms - 20ms & rexmt in same path & TBC                &  \\\hline
Tail drop 3 & 20ms - 20ms & rexmt in same path & TBC                &  \\ \hline
\end{tabular}
\end{table}

\begin{table}[]
\centering
\caption{Tail loss scenarios with tcp.early.retrans = 0 ER disabled}
\label{ret3}
\begin{tabular}{|l|l|l|l|l|}
\hline
 testcase   & Asymmetry   & Metalevel          & Subflowlevel       &  \\\hline
Tail drop 1 & 20ms - 30ms & rexmt in same path & rexmt in same path &  \\\hline
Tail drop 2 & 30ms - 20ms & rexmt in same path & TBC                &  \\\hline
Tail drop 3 & 20ms - 20ms & rexmt in same path & TBC                & \\ \hline
Tail drop 4 & 20ms - 120ms &  			&		&  \\ \hline
Tail drop 5 & 120ms - 20ms &  			& 		& \\ \hline 
\end{tabular}
\end{table}

\begin{table}[]
\centering
\caption{Tail loss scenarios with tcp.early.retrans = 4 TLP disabled}
\label{ret3}
\begin{tabular}{|l|l|l|l|l|}
\hline
 testcase   & Asymmetry   & Metalevel          & Subflowlevel       &  \\\hline
Tail drop 1 & 20ms - 30ms & rexmt in same path & rexmt in same path &  \\\hline
Tail drop 2 & 30ms - 20ms & rexmt in same path & TBC                &  \\\hline
Tail drop 3 & 20ms - 20ms & rexmt in same path & TBC                & \\ \hline
\end{tabular}
\end{table}

>>>>

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

% Title Page
\title{Loss recovery and tail loss performance in Multipath TCP}
\author{KAU}

@@

We try to understand the loss recovery and retransmission policies in state of the art MPTCP linux implementation. As per the specification of Multipath TCP introduced in 
MPTCP features acknowledgements at connection-level as well as
   subflow-level acknowledgements, in order to provide a robust service
   to the application.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth]{images/fortest.pdf}
\caption{Topology used for Emulation}\label{fig1}
\end{center}
\end{figure}
\begin{center}

\begin{table}
\begin{center}
\begin{tabular}{|c|cccccccccc|}
      \hline
      \multicolumn{1}{c}{} & & \\[\dimexpr-\normalbaselineskip-\arrayrulewidth]
      \textbf{Burst Size} & \multicolumn{10}{c|}{160 Packets} \\
      \hline
      \textbf{Separation Time} & \multicolumn{10}{c|}{2s} \\
      \hline

@@

\subsection{Testing with Deterministic loss patterns}
In order to understand the retransmission behavior of the Linux MPTCP implementation and to reproduce the observed retransmissions, we use a deterministic drop pattern.
Losses generated by using associating netem with corresponding interfaces and dropping the packets(Cite KAU paper).\ref{timing}\ref{1p}\ref{1pp}\ref{2p}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timing.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios}\label{timing}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth,natwidth=578.16,natheight=433.62]{plots/1P.pdf}
\caption{Single packet tail loss}\label{1p}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=578.16,natheight=433.62]{plots/1PP.pdf}
\caption{Single packet tail loss together with probe loss}\label{1pp}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth,natwidth=578.16,natheight=433.62]{plots/2P.pdf}
\caption{Two packet tail loss}\label{2p}
\end{center}
\end{figure}

@@

\begin{table}[!ht]
\centering
\caption{Tail loss scenarios with tcp.early.retrans = 3 default}
\label{ret3}
\begin{tabular}{|l|l|l|l|l|}
\hline
 testcase   & Asymmetry   & Metalevel          & Subflowlevel       &  \\\hline
Tail drop 1 & 20ms - 30ms & rexmt in same path & rexmt in same path &  \\\hline
Tail drop 2 & 30ms - 20ms & rexmt in same path & TBC                &  \\\hline
Tail drop 3 & 20ms - 20ms & rexmt in same path & TBC                &  \\ \hline
\end{tabular}
\end{table}

\begin{table}[!ht]
\centering
\caption{Tail loss scenarios with tcp.early.retrans = 0 ER disabled}
\label{ret0}
\begin{tabular}{|l|l|l|l|l|}
\hline
 testcase   & Asymmetry   & Metalevel          & Subflowlevel       &  \\\hline
Tail drop 1 & 20ms - 30ms & rexmt in same path & rexmt in same path &  \\\hline
Tail drop 2 & 30ms - 20ms & rexmt in same path & TBC                &  \\\hline
Tail drop 3 & 20ms - 20ms & rexmt in same path & TBC                & \\ \hline
Tail drop 4 & 20ms - 120ms &  			&		&  \\ \hline
Tail drop 5 & 120ms - 20ms &  			& 		& \\ \hline 
\end{tabular}
\end{table}

\begin{table}[!ht]
\centering
\caption{Tail loss scenarios with tcp.early.retrans = 4 TLP disabled}
\label{ret4}
\begin{tabular}{|l|l|l|l|l|}
\hline
 testcase   & Asymmetry   & Metalevel          & Subflowlevel       &  \\\hline
Tail drop 1 & 20ms - 30ms & rexmt in same path & rexmt in same path &  \\\hline
Tail drop 2 & 30ms - 20ms & rexmt in same path & TBC                &  \\\hline
Tail drop 3 & 20ms - 20ms & rexmt in same path & TBC                & \\ \hline
\end{tabular}
\end{table}
